A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Material

### 2018-11-23 MS.tex
Read up till `Analysis of censored data series' section

To compare the two methods, we converted numbers of gonotrophic cycle
(physiological age) into lifespan (chronological age) as described in
the SOM using estimates of gonotrophic cycle duration (Fig. \ref{S-fig:dissection_gonotrophicCycleRaw}). Table \ref{S-tab:dissection_estimated_lifespans_chron} provides posterior summaries of chronological for the species and genera in the dissection dataset. For ten species, we had enough data from both species to make a comparison, and there was a positive correlation (not
statistically significant; Pearson correlation $\rho=0.42$, $n=10$, $p=0.23$)
between the two measures (Fig. \ref{fig:comparison}), and in only one case -- for \emph{A.
darlingi} - there was a significant difference in the
time-series level LBLs (Table \ref{S-tab:comparison}).

>>>>

To compare the two methods, we converted numbers of gonotrophic cycle
(physiological age) into lifespan (chronological age) as described in
the SOM using estimates of gonotrophic cycle duration (Fig. \ref{S-fig:dissection_gonotrophicCycleRaw}). Table \ref{S-tab:dissection_estimated_lifespans_chron} provides posterior summaries of chronological for the species and genera in the dissection dataset (see also Fig. ). For ten species, we had enough data from both species to make a comparison, and there was a positive correlation (not
statistically significant; Pearson correlation $\rho=0.42$, $n=10$, $p=0.23$)
between the two measures (Fig. \ref{fig:comparison}), and in only one case -- for \emph{A.
darlingi} - there was a significant difference in the
time-series level LBLs (Table \ref{S-tab:comparison}).

### 2018-11-23 supplementary_materials.tex
Sorted table references
Read up till `Analysis of censored data series' section

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

@@

The estimates of mean mosquito lifespan that we present here (Fig. \ref{fig:dissection_lifespan_gonotrophic}) resulted from the use of the exponential survival model (i.e. no age dependence). This choice was made because we found limited evidence in support of age-dependent mortality (see Section \ref{sec:dissection_ageDependence}). However, since the priors for each of the survival functions were specified to allow for a wide variety of lifespans (Fig. \ref{fig:dissection_lifespanPriorsParity}) the specific choice of survival function made little difference to resultant estimates (data not shown).

To demonstrate that the results we obtain are not sensitive to the particular form of hierarchical prior structure chosen we also provide estimates of the lifespan for each series analysed on its own. To do so we assume priors on the rate parameter of the exponential distribution that provides support over a wide range of possible lifespans (Fig. \ref{fig:dissection_lifespanPrior_individual}A). We also specified a prior on the over-dispersion parameter $\kappa$ that was comparable to the hierarchical case (Fig. \ref{fig:dissection_lifespanPrior_individual}B).

@@

\subsubsection{Chronological lifespan estimates}
\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential_chron.pdf}}
	\caption{\textbf{Posterior estimates of female mosquito mean chronological lifespan across species, genus and overall groupings as determined from the dissection data.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential}
\end{figure}

>>>>

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thesection}{S\arabic{section}}

@@

The estimates of mean mosquito lifespan that we present here (Fig. \ref{fig:dissection_lifetimes_exponential}) resulted from the use of the exponential survival model (i.e. no age dependence). This choice was made because we found limited evidence in support of age-dependent mortality (see `Results'). However, since the priors for each of the survival functions were specified to allow for a wide variety of lifespans (Fig. \ref{fig:dissection_lifespanPriorsParity}) the specific choice of survival function made little difference to resultant estimates (data not shown).

To demonstrate that the results we obtain are not sensitive to the particular form of hierarchical prior structure chosen we also provide estimates of the lifespan for each series analysed separately (i.e. non-hierarchically). To do so we assume priors on the rate parameter of the exponential distribution that provides support over a wide range of possible lifespans (Fig. \ref{fig:dissection_lifespanPrior_individual}A). We also specified a prior on the over-dispersion parameter $\kappa$ that was comparable to the hierarchical case (Fig. \ref{fig:dissection_lifespanPrior_individual}B).

@@

\subsubsection{Chronological lifespan estimates}
\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential_chron.pdf}}
	\caption{\textbf{Posterior estimates of female mosquito mean chronological lifespan across species, genus and overall groupings as determined from the dissection data.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential_chron}
\end{figure}
